### 2020-04-16 paper.tex
Refine Outline

\newcommand{\version}{v0.1 Outline}

@@

	\Large{Workshop Paper}
	\par
	\Huge{tbd. ``Reactive Debugging for modern Frontend Web Applications''}
	\par
	\vspace{2ex}

@@

\section{Overview}
\begin{itemize}
	\item What is RP?
	\item What is debugging?
	\item Debug concepts in RP
	\item Research so far
	\item Tooling development so far
	\item Research questions:
	\begin{itemize}
		\item RQ1 How do web frontend engineers debug RP code?
		\item RQ2 How can we improve the debugging experience for FE?
		\item RQ3 Does a specific RP debugger for FE improve the debugging experience?
	\end{itemize}
	\item \bf{DEBUGGING EXPERIENCE: How to measure? Use ``time'' instead?}
\end{itemize}

\section{``Current State''}
\begin{itemize}
	\item Closer look to past Research
	\item \dots and the tools which were built based on it
	\item Pick up gaps/deficiencies from past research/tools

\end{itemize}

\section{Interviews}
\begin{itemize}
	\item Answer RQ1
	\item Reference previous research
	\item Present results of own informal interviews
	\begin{itemize}
		\item Validate/invalidate results of past research based on interviews
	\end{itemize}
	\item Lead over to frontend engineering
	\item Compose past research with interview results
\end{itemize}

\section{Solution Design}
\begin{itemize}
	\item Work out concepts for FE debugger tooling to answer RQ2
	\item What do we want to improve compared to existing/previous approaches?
	\item Lay out user stories
\end{itemize}

\section{Study Design}
\begin{itemize}
	\item Propose ways how to validate the proposed solution in order to answer RQ3
\end{itemize}

\section{Threats to Validity}
\begin{itemize}
	\item Informal interviews only
	\begin{itemize}
		\item Describe background of interview partners
		\item Frontend engineering heavy
	\end{itemize}
	\item Real study to validate/reassure?
\end{itemize}

@@

\bibliographystyle{splncs04}
\bibliography{index.bib}

>>>>

\newcommand{\version}{v0.2 Draft}

@@

	\Large{Workshop Paper}
	\par
	\Huge{Debugging of Modern RxJS-based Frontend Web Applications}
	\par
	\vspace{2ex}

@@

\section{Introduction}

\emph{Brief summary over this paper}

\emph{What is RP?}

\emph{What is debugging?}

\emph{Debug concepts in RP}

\emph{Research so far}

\emph{Tooling development so far}

\emph{Conclude with Research Questions}

\begin{itemize}
	\item \emph{RQ1: What challenges do frontend engineers face when debugging RxJS based code?}
	\item \emph{RQ2: How can the experience of frontend engineers during debugging of RxJS based code be improved?}
	\item \emph{RQ3: What is the impact of a proposed solution on the debugging experience of a frontend engineer?}
\end{itemize}

\subsection{Reactive Programming with RxJS}

\subsection{Debugging Concepts}
\begin{itemize}
	\item Imperative
	\item Declarative
	\item Omniscient
\end{itemize}

\subsection{Specialized Reactive Programming Tooling}

\begin{itemize}
	\item Brief overview on specific tooling
	\item For frontend, but also other tiers
	\item Rxviz \footnote{\url{https://rxviz.com/}} see also \url{https://rxviz.com/feedback} for input?
	\item rxjs-spy \footnote{\url{https://github.com/cartant/rxjs-spy}}
	\item rxfiddle \cite{10.1145/3180155.3180156}
	\item reactive-inspector \cite{10.1145/2884781.2884815}
	\item TOD \cite{5287015}
\end{itemize}

\section{Interviews and War Stories}
\begin{itemize}
	\item We answer RQ1 here
	\item Present results of own informal interviews
	\item Combine with war stories
	\item Extract 3 main challenges
\end{itemize}

\section{Discussion}
\begin{itemize}
	\item Closer look to past Research
	\item \dots and the tools which were built based on it
	\item Set up war story extract to be replicated with existing tooling
\end{itemize}

\section{Study Design}
\begin{itemize}
	\item Use prev section to build experiments using existing tooling
	\item Validate stories and interviews
\end{itemize}

\section{Future Work}
\begin{itemize}
	\item Pick up results from war stories and experiment
	\item Propose one solution per challenges
	\item Sketch how this could look like
	\item This answers RQ2
\end{itemize}

\section{Threats to Validity}
\begin{itemize}
	\item Informal interviews/war stories only
	\begin{itemize}
		\item Describe background of interview partners
		\item Frontend engineering heavy
	\end{itemize}
\end{itemize}

@@

\bibliographystyle{splncs04}
\bibliography{bibliography.bib}
